A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-07-29 latex/paper.tex
Modified regression slopes wording

Figure~\ref{fig:inc_tt_worker} shows the total execution time of the
Incrementation application, broken down into data transfer (read and
write), compute (sleep), and overhead time. As expected, the computing time
stays similar when the number of workers increases. However, the data
transfer time and overhead increase proportionally to the number of
workers with regression lines:

\hspace{1cm}\(\hat{y}=2336.9499\cdot{x} + 325.00574\) (Spark)

\hspace{1cm}\(\hat{y}=2650.13505\cdot{x} + 1585.37218\) (Bag)

\hspace{1cm}\(\hat{y}=3250.53406\cdot{x} + 1769.50351\) (Delayed)

\hspace{1cm}\(\hat{y}=3570.39758\cdot{x} + 1062.23031\) (Futures)

@@

In Figure~\ref{fig:bids_tt_worker}, the total execution time of each function is
shown. Each engine has a similar total time independently of its number of workers.
This is due to the, almost, linear scaling of the engines. The overhead increases
proportionally with the number of workers (see regression lines below). This is due
to more communication between the scheduler and workers as well as intra-worker and
inter-worker communication.

\hspace{1cm}\(\hat{y}=223.53586\cdot{x} + 91.616964\) (Spark)

\hspace{1cm}\(\hat{y}=182.82659\cdot{x} - 11.43834\) (Bag)

\hspace{1cm}\(\hat{y}=172.54183\cdot + 400.69433\) (Delayed)

\hspace{1cm}\(\hat{y}=132.41481\cdot{x} + 90.32813\) (Futures)

>>>>

Figure~\ref{fig:inc_tt_worker} shows the total execution time of the
Incrementation application, broken down into data transfer (read and
write), compute (sleep), and overhead time. As expected, the computing time
stays similar when the number of workers increases. However, the data
transfer time and overhead increase proportionally to the number of
workers with regression slopes: Spark (\SI{2337}{\second/task}), Bag
(\SI{2650}{\second/task}), Delayed (\SI{3251}{\second/task}), Futures
(\SI{3570}{\second/task}).

@@

In Figure~\ref{fig:bids_tt_worker}, the total execution time of each function is
shown. Each engine has a similar total time independently of its number of workers.
This is due to the, almost, linear scaling of the engines. The overhead increases
proportionally to the number of workers with regression slopes: Spark
(\SI{224}{\second/task}), Bag (\SI{183}{\second/task}), Delayed
(\SI{173}{\second/task}), Futures (\SI{132}{\second/task}). This is due to more
communication between the scheduler and workers as well as intra-worker and
inter-worker communication.
